Probability Distribution Checks

### 2017-06-15 Probability_distribution_checks.Rmd
Add probability distribution checks for all data

## 2015

@@

#### Normal

```{r 2015_inc_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$TShB_inc_AUDPS, "norm")
plot(f1)

@@

#### Exponential

```{r 2015_inc_exp, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(AUDPS15$TShB_inc_AUDPS, "exp")
plot(f1)
car::qqp(AUDPS15$TShB_inc_AUDPS, "exp")
car::qqp(AUDPS15$TShB_inc_AUDPS, "lnorm")

```

@@

#### Normal

```{r, 2016_inc_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS16 <- subset(AUDPS, YEAR == "2016")
 f1 <- fitdist(AUDPS16$TShB_inc_AUDPS, "norm")
plot(f1)

@@

#### Exponential

```{r 2016_inc_exp, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(AUDPS16$TShB_inc_AUDPS, "exp")
plot(f1)

car::qqp(AUDPS16$TShB_inc_AUDPS, "exp")
```

@@

The 2015 data fit an exponential distribution while the 2016 data fit a normal distribution.

>>>>

@@

#### Tiller Incidence Normal

```{r 2015_TShB_inc_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$TShB_inc_AUDPS, "norm")
plot(f1)

@@

#### Tiller Incidence Exponential

```{r 2015_TShB_inc_exp, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(AUDPS15$TShB_inc_AUDPS, "exp")
plot(f1)
car::qqp(AUDPS15$TShB_inc_AUDPS, "exp")
```

#### Tiller Severity Normal

```{r 2015_TShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$TShB_sev_AUDPS, "norm")
plot(f1)

car::qqp(AUDPS15$TShB_sev_AUDPS, "norm")
```

#### Tiller Severity Exponential

```{r 2015_TShB_sev_exp, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(AUDPS15$TShB_sev_AUDPS, "exp")
plot(f1)
car::qqp(AUDPS15$TShB_sev_AUDPS, "exp")
```

#### Leaf Severity Normal

```{r 2015_LShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$LShB_sev_AUDPS, "norm")
plot(f1)

car::qqp(AUDPS15$LShB_sev_AUDPS, "norm")
```

#### Leaf Severity Exponential

These data do not fit this distribution, all values must be positive.

@@

#### Tiller Incidence Normal

```{r 2016_TShB_inc_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS16 <- subset(AUDPS, YEAR == "2016")
f1 <- fitdist(AUDPS16$TShB_inc_AUDPS, "norm")
plot(f1)

@@

#### Tiller Incidence Exponential

```{r 2016_TShB_inc_exp, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(AUDPS16$TShB_inc_AUDPS, "exp")
plot(f1)
car::qqp(AUDPS16$TShB_inc_AUDPS, "exp")
```

#### Tiller Severity Normal

```{r 2016_TShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS16 <- subset(AUDPS, YEAR == "2016")
f1 <- fitdist(AUDPS16$TShB_sev_AUDPS, "norm")
plot(f1)

car::qqp(AUDPS16$TShB_sev_AUDPS, "norm")
```

#### Tiller Severity Exponential

```{r 2016_TShB_sev_exp, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(AUDPS16$TShB_sev_AUDPS, "exp")
plot(f1)
car::qqp(AUDPS16$TShB_sev_AUDPS, "exp")
```

#### Leaf Severity Normal

```{r 2016_LShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
AUDPS16 <- subset(AUDPS, YEAR == "2016")
f1 <- fitdist(AUDPS16$LShB_sev_AUDPS, "norm")
plot(f1)

car::qqp(AUDPS16$LShB_sev_AUDPS, "norm")
```

#### Leaf Severity Exponential

```{r 2016_LShB_sev_exp, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(AUDPS16$LShB_sev_AUDPS, "exp")
plot(f1)
car::qqp(AUDPS16$LShB_sev_AUDPS, "exp")
```

@@

The 2016 data fit an exponential distribution while the 2016 data fit a normal distribution.
